Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2021-03-29 rebuttal/ijcai21-authors-response.tex
Last for now!

	We thank the reviewers for their comments. We specify that the questions reported are not verbatim for lack of space and focus on factual errors. 
\paragraph{Review $\#$2 writes as a weakness that “the method proposed here is not compared with others”.}
We believe it is erroneous to consider the lack of comparison a weakness. The simultaneous elicitation of both the voting rule and the agents preferences is a novel setting and, as far as we know, there is no competitor from the state-of-the-art to compare with. 
We are not aware of any method that elicits the voting rule we could compare with – the work by Cailloux and Endriss [2014] does not consider PSRs. Nevertheless, the Two Phases strategy was designed to challenge our interleaving approach by comparing it with a more classical sequential method, which (when first eliciting the rule and then the agents preferences) coincides with the method of Lu and Boutilier [2011] for preferences elicitation with a fixed voting rule.
%\paragraph{Review $\#$2: “Only variants of the same methods are compared with each others”.}
%\commentOC{Isn’t this a bit arguable that Elitist is very different rather than a variant?}
The Elitist strategy has a very different approach than the Pessimistic one, to the point that it cannot be considered a variant. They are compared in a situation specifically tailored to advantage the Elitist.

@@

\paragraph{Review $\#$56: Can you clarify better the rationale behind the assumptions you make on questions to the chair?}
The question is asked by showing a profile and asking who should win; the response is encoded as a constraint and added to the system’s knowledge. Phrasing questions in terms of winners out of profiles is arguably the most fundamental and natural view of what a social choice function is (as pointed out in our response to reviewer $\#$32). We adapt a mechanism used in a real life experiment by Giritligil et al. [2005] in a novel way for the elicitation of PSRs.
%Note that we want to ask an informative query: the elicitation strategy decides which question to be asked, and, if it is of the “chair” type, the strategy decides the linear constraint to check; this is then translated to a profile.

@@

\paragraph{Review $\#$56 writes that we “assume the human chair will answer hundreds of questions”. \commentOC{Beatrice, please check the exact quote.}}
%We assume the chair to be human and, as discussed in the paragraph “Building concrete questions for the chair“ on page 3, we view questions “what is the winner of this profile” to be easier to answer than directly asking the weights (in the same way as, for the problem of elicitation an utility function, one would ask comparison queries rather than asking directly utility values). 
We do not assume this. We plot the total number of questions in order to have a simple way to compare the total elicitation cost. 
\commentOC{I’d remove this first sentence and rephrase the next one.}
Table 1 of Appendix shows that the number of questions posed to the chair (and each agent) is usually small. Our experiments also show efficiency decreases slowly when diminishing the number of questions to the chair and distributing them to the voters instead.
%When the profile is quite homogeneous (see the lines corresponding to real datasets) this number is very low or even zero in case of clear winner. We also mention that the process could be terminated early: after a fixed number of questions (the “approximate winner” is the alternative with lowest regret); or after reaching a "low enough" regret.
%In fact the number of questions asked to the chair using the Pessimistic strategy (as shown in the appendix) is often quite small  (e.g. zero in skate and "courses", 8.4 in m5n10, 13 in m5n20, 30 in tshirt,...), this is because the strategy does a good job of asking the question that gives more information, and often only “sparse” information about the voting rule is enough. Similarly, the average number of questions asked to a voter is also reasonable (e.g questions per agent 6.5 in courses, 6.1 in m5n10,  )
%: X.X in Experiment YY, for instance. In Table 2, the (10,20) example shows that to reach a “low” regret -that we define as n/10- we need to ask 340 questions. This number should be divided among the voters and the chair, resulting in ~ 10 questions per voter, which we consider a reasonable amount. The fact that asking too many questions to the chair is not worth it isworth is also displayed in Table 3 in the main text.
%Finally, note that the process could be terminated early: e.g. one could decide to stop after a fixed number of questions (even if regret is not zero) and to output as an “approximate winner” the alternative with lowest minimax regret value.
%If the paper will be accepted, we will stress more this point and include the Appendix Table in the final version.
\end{document}

>>>>

	We thank the reviewers for their comments. We focus on factual errors and on the “questions for the authors”.

\paragraph{Review $\#$2 writes as a weakness that “the method proposed here is not compared with others”.}
We believe it is erroneous to consider the lack of comparison a weakness. The simultaneous elicitation of both the voting rule and the agents preferences is a novel setting and, as far as we know, there is no competitor from the state-of-the-art to compare with. 
We are not aware of any method that elicits the voting rule we could compare with – the work by Cailloux and Endriss [2014] does not consider PSRs. Nevertheless, the Two Phases strategy was designed to challenge our interleaving approach by comparing it with a more classical sequential method, which (when first eliciting the rule and then the agents preferences) coincides with the method of Lu and Boutilier [2011] for preferences elicitation with a fixed voting rule.
%\paragraph{Review $\#$2: “Only variants of the same methods are compared with each others”.}
%\commentOC{Isn’t this a bit arguable that Elitist is very different rather than a variant?}
The Elitist strategy has a very different approach than the Pessimistic one, to the point that it cannot be considered a variant. They are compared in a situation specifically tailored to advantage the Elitist.

@@

@@

\paragraph{Review $\#$56: “Can you clarify better the rationale behind the assumptions you make on questions to the chair?”}
The question is asked by showing a profile and asking who should win; the response is encoded as a constraint and added to the system’s knowledge. Phrasing questions in terms of winners out of profiles is arguably the most fundamental and natural view of what a social choice function is (as pointed out in our response to reviewer $\#$32). We adapt a mechanism used in a real life experiment by Giritligil et al. [2005] in a novel way for the elicitation of PSRs.
%Note that we want to ask an informative query: the elicitation strategy decides which question to be asked, and, if it is of the “chair” type, the strategy decides the linear constraint to check; this is then translated to a profile.

\paragraph{Review $\#$56: “You say that you assume the chair to be human, yet you think he will answer hundreds of questions..?”}
%We assume the chair to be human and, as discussed in the paragraph “Building concrete questions for the chair“ on page 3, we view questions “what is the winner of this profile” to be easier to answer than directly asking the weights (in the same way as, for the problem of elicitation an utility function, one would ask comparison queries rather than asking directly utility values). 
We do not assume this. We plot the total number of questions in order to have a simple way to compare the total elicitation cost. 
Table 1 of Appendix shows that the number of questions posed to the chair (and each agent) is usually small. Our experiments also show that efficiency decreases only slowly when diminishing the number of questions to the chair and distributing them to the voters instead.
%When the profile is quite homogeneous (see the lines corresponding to real datasets) this number is very low or even zero in case of clear winner. We also mention that the process could be terminated early: after a fixed number of questions (the “approximate winner” is the alternative with lowest regret); or after reaching a "low enough" regret.
%In fact the number of questions asked to the chair using the Pessimistic strategy (as shown in the appendix) is often quite small  (e.g. zero in skate and "courses", 8.4 in m5n10, 13 in m5n20, 30 in tshirt,...), this is because the strategy does a good job of asking the question that gives more information, and often only “sparse” information about the voting rule is enough. Similarly, the average number of questions asked to a voter is also reasonable (e.g questions per agent 6.5 in courses, 6.1 in m5n10,  )
%: X.X in Experiment YY, for instance. In Table 2, the (10,20) example shows that to reach a “low” regret -that we define as n/10- we need to ask 340 questions. This number should be divided among the voters and the chair, resulting in ~ 10 questions per voter, which we consider a reasonable amount. The fact that asking too many questions to the chair is not worth it isworth is also displayed in Table 3 in the main text.
%Finally, note that the process could be terminated early: e.g. one could decide to stop after a fixed number of questions (even if regret is not zero) and to output as an “approximate winner” the alternative with lowest minimax regret value.
%If the paper will be accepted, we will stress more this point and include the Appendix Table in the final version.
\end{document}
